---
title: "Presentacion Template"
author: "Ignacio Spiousas y Pablo Etchemendy"
date: "April 18, 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = '')
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(echo = FALSE)
library(palmerpenguins)
library(tidyverse)
```

## New Slide
```{r}
penguins %>% group_by(species) %>%
  ggplot(aes(x=species, y=body_mass_g, colour=species, fill=species)) +
    geom_point() + 
    theme_minimal()
  
```

## Formula

$$
f(x) = \beta_0 + \beta_1 x + \beta_2 x^2 + \beta_3 x^3 + \beta_4 (x-\xi)^3_+
$$
$$
(x-\xi)^3_+ =
\begin{cases}
 (x-\xi)^3\, ,& x>\xi \\
 0  ,& x\leq\xi
 \end{cases}       
$$

$$
\begin{aligned}
  (x \leq \xi) \Rightarrow f(x) &= \beta_0 + \beta_1 x + \beta_2 x^2 + \beta_3 x^3 \\
  (x > \xi) \Rightarrow f(x) &= \beta_0 + \beta_1 x + \beta_2 x^2 + \beta_3 x^3 + \beta_4(x^3 -3x^2\xi + 3x\xi^2 - \xi^3) \\
  &=(\beta_0 + \beta_4\xi^3) + (\beta_1 + 3\beta_4\xi^2)x + (\beta_2 - 3\beta_4)
\end{aligned}
$$

## My title
- Bullet one
- Bullet two

1. Item a
2. Item b

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

